%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%----------------------------------------------------------------------------------------
 
\documentclass{resume} % Use the custom resume.cls style 
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    bookmarks=true,
    pdfpagemode=FullScreen,
    }
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
 
\usepackage[dvipsnames]{xcolor}
\colorlet{LightRubineRed}{RubineRed!70!}
\colorlet{Mycolor1}{green!10!orange!90!}
\definecolor{Mycolor2}{HTML}{00F9DE}
    
\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{ \href{http://www.abhinitmz.tk/}{ABHISHEK}  SHARMA} % Your name 
\address{Boys Hostel-3, NIT Mizoram, Aizawl, Mizoram, 796025} % Your address 
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional) 
\address{+91 7005693645  \\  5h1dabhi@gmail.com \\   Github://\href{https://github.com/abhi1d}{abhi1d}  \\  LinkedIn://\href{https://www.linkedin.com/in/abhi1d/}{abhi1d}  }                        

\begin{document}  

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Engineering in Computer Science and Engineering} \hfill {July 2015- Present}
\\ 
National Institute of Technology Mizoram,  CGPA: 8.66/10.00   

{\bf HSC, Class XII} \hfill {June 2012 - April 2014}
\\ 
Vikas Vidhya Ashram Sr. Sec. School, Jaipur, Rajasthan, 87.80\%

{\textbf{SSC, Class X}}  \hfill{June 2010 - April 2012}\\
Vikas Vidhya Ashram Sr. Sec. School, Jaipur, Rajasthan, 79.83\%    
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection} 

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
Programming Languages  :&\textit{Proficient} - Java, JSP(Java Server Pages), C\\
                       &\textit{Intermediate} -  C++, Python, HTML, Bootstrap-3\\
                       
                       &\textit{Familiar} - \LaTeX, JavaScript, CSS, JSON, AJAX, Markdown, JQuery, Mysql,\\
                       & Firebase
                       \\
Tools/Frameworks  :&  Spring Framework, Android Studio, Git,IntelliJ IDEA, VS Code, Firebase,\\  
                   &  Apache Tomcat, Web Scraping, FileZilla, JDBC, JDOM Parser, Eclipse \\
                   &  Amazon Web Services(AWS), linux hosting - Cpanel etc.
                       
                        
                                
 
\end{tabular}   

\end{rSection}

%-------------------------------------------------------------------------------
% Course Work


\begin{rSection}{CourseWork}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
Academics : & Data Structure ,Design and analysis of Algorithm ,System programming, Theory of \\ 
          & Computation, Linear algebra, Probability theory, Operating System, DBMS, Software Engineering.\\

\end{tabular}   

\end{rSection}

%	INTERNSHIP 
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCES} \itemsep -3pt  

{\textbf{Winter Internship - Indian Institute of Technology Patna }  } \hfill December 2017 - January 2018{}{} 
\begin{itemize}
\item Extraction of some information from the XML formated research papers using DOM parser.
\item Implemented the features for Machine Learning \& NLP project.
\item \textbf{Tools/Frameworks Used : } Java, Swing Framework, DOM \& JSON Parser, Web Scraping,Eclipse IDE, Grobid etc. 
\item Other information cannot be revealed for confidential purposes.
\end{itemize}
\end{rSection}  

%-------------------------------------------------------------------------------
%	PROJECTS

\begin{rSection}{PROJECTS}
{\textbf{Capture The Flag | \href{https://github.com/abhi1d/capture-the-flag}{Github}}} \hfill April 2018{}{} 
\begin{itemize}
\item Built the online platform for capture the flag game. 
\item It contains set of questions and all the questions have a unique flag to crack the questions.
\item Some set of questions redirect to the web pages for the flag of the questions. 
\item Dashboard section in the game has all the responses to the questions of each player and one player can see only his responses.
\item Winners determined at the end of the CTF, the player that ends with the most points will be            declared the winner. In case of tie, the winner will be the one who solved the questions in least       time.
\item \textbf{Tools :} IntelliJ IDEA, AWS Codestar, Spring-MVC Framework, JSP, Java, Apache Tomcat.
\item \textbf{Services : }Amazon Web Services
\end{itemize}

%-----------------------------------------------------

{\textbf{Attendance Manager | \href{https://github.com/abhi1d/Attendance-Manager}{Github}}} \hfill August 2017 - November 2017{}{} 
\begin{itemize}
\item Created a Dynamic web application for Managing student attendance using Java EE technology. 
\item It stores the user information in Mysql database.
\item It shows alert when the attendance falls below 75\%.
\item \textbf{Tools :} Eclipse IDE, Java, JSP, JDBC, Mysql, Tomcat Server.
\end{itemize}

%------------------------------------------------

{\textbf{Om Construction | \href{https://github.com/abhi1d/OmConstruction}{Github}}} \hfill May 2017 - June 2017{}{} 
\begin{itemize}
\item It is organization mobile android application for Om Construction named company who was facing problem to organize data.
\item In this App, they can see updated details of any product and they can secure their data.
\item Graphs are generated for all the products with respect to its value which can help to understand the sales of the product.
\item \textbf{Tools :}  Java, Android Studio, Firebase, Maven Graph Library
\end{itemize}

%-------------------------------------------------

{\textbf{Random Quote Generator | \href{https://codepen.io/geekabhi007/pen/RgqBZX}{CodePen} }} \hfill July 2017{}{} 
\begin{itemize}
\item It is Web App where if anyone presses “Generate” button then every time new quotes will appear and \\accordingly UI changes will happen.
\item We can tweet our new generated quotes. 
\item \textbf{Tools :}  Html, CSS ,Bootstrap v3, QuotesOnDesign API, Twitter API, JavaScript, Jquery, Ajax. 
\end{itemize}

 



%--------------------------------------------------------------------------------------
\end{rSection}  %End of the project section


% Extra-Cirrucular
%--------------------------------------------------------------------------------------

\begin{rSection}{ACHIEVEMENTS \&  AWARDS} \itemsep -2pt   

\begin{itemize}
 \item \textbf{WINNER - Web Development Event} - Morphosis 2017 Event at NIT Mizoram.
 \item \textbf{Got 458 rank } in RPET 2015 (State Board Engineering Entrance Exam).
 \item \textbf{Selected For SHE(Scholarship For High Education)} in High School, 2014.
 \item \textbf{Got laptop} from Rajasthan Govt. as a topper of rajasthan, 2012.
 \item \textbf{Secured 100\% Marks in Maths}, Subject merit, 2012.

\end{itemize}  


\end{rSection} 

\begin{rSection}{ Hobbies  } \itemsep -3pt        
\begin{itemize}
\item Listening Music.
\end{itemize}
\end{rSection}

%---------------------------------------------------------------------------------
%  DECLARATION
%--------------------------------------------------------------------------------


\end{document}
